---
title: "Shiny App Documentation"
author: "Deepanshu Rustagi"
date: "8/9/2020"
output:
  html_document: default
  pdf_document: default
---
### Documentation
This app is intended to present some insights from mtcars data when the user selects the number of cylinders - 4, 6 or 8.

A plot of the the mpg variable for the filtered data set is plotted in an interactive manner.

Also, the maximum Horse Power and Weight for the selected cylinder number is also presented.

This is the formal documentation of this Shiny App.

The app is hosted on Rstudio server using shinyapps.io at the following URL: https://deepanshur.shinyapps.io/shinyassignmentapp/

The URL for the repository containing the ui.R and server.R code files along with this documentation file is: https://github.com/deepanshur3006/ShinyAppAssignment

### Code for ui.R and server.R

**ui.R**
```{r eval=FALSE}
library(webshot)
library(shiny)
library(dplyr)
data(mtcars)
shinyUI(fluidPage(
    titlePanel("Interesting mtcars Analysis"),
    sidebarLayout(
        sidebarPanel(
            h3('Choose the number of cylinders'),
            radioButtons("cyl", "Number of Cylinders", 
                         choices = c(4,6,8))
            
            
        ),
        mainPanel(
            h3('Here is some trivia!'),
            h3('MPG Values For Selected Cars'),
            plotOutput("plot1"),
            h3('Maximum Horse Power'),
            textOutput("maxhp"),
            h3("Maximum Weight"),
            textOutput("maxwt"),
            h3('Documentation for using app: https://rpubs.com/deepanshu_rustagi88/647435')
        )
    )
))
```
**server.R**
```{r eval=FALSE}
library(webshot)
library(shiny)
library(dplyr)
data(mtcars)
shinyServer(function(input, output) {
    
    
    filterdata<- reactive({
        
        tempdf<- filter(mtcars,cyl==input$cyl)
        
    }) 
    
    
    output$plot1 <-  renderPlot({
        
        
        plot(filterdata()$mpg,xlab = 'MPG Values', ylab = 'Indexes', 
        main = 'MPG of Cars Having Selected
                   Number of Cylinders')
        
    })
    
    output$maxhp <- renderText({
        
        max(filterdata()$hp) 
        
    })
    
    output$maxwt <- renderText({
        max(filterdata()$wt)
        
    })
    
    
})
```

    